---
title: "Static Report"
author: "Rohit Shivthare"
date: "October 2023"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, comment="", warning = FALSE, message = FALSE, tidy.opts=list(width.cutoff=55), tidy = TRUE)

library(data.table)
library(DT)
library(dplyr)
library(tidyverse)
library(rmarkdown)
library(ggplot2)
library(broom)
```

```{r source}
source("constants.R")
source("functions.R")
```

```{r read_data}
survey <- fread("../Data/mobile phone survey data.csv")
```

```{r constants}

```

```{r functions}

```


```{r explore_data, eval = FALSE}
# To understand the structire of survey data
str(survey)

# To check the first 5 rows of data
head(survey)

# To find the unique values of respondent variables
unique(survey$Gender)
unique(survey$Region)
unique(survey$Persona)
unique(survey$Product)
```


# Calculations {.tabset}


### Q1: Respondent Variables {.tabset}

#### Age Group

```{r q1_age.group}
find_percentage(survey, Age.name)
```

#### Gender

```{r q1_gender}
find_percentage(survey, Gender.name)
```

#### Income Group

```{r q1_income.group}
find_percentage(survey, Income.name)
```

#### Region
 
```{r region}
find_percentage(survey, Region.name)
```

#### Persona

```{r persona}
find_percentage(survey, Persona.name)
```


### Q2:  Segmented Outcomes {.tabset}

#### Part A

What are the top 5 products by Awareness rates in the Northeast?

```{r q2_a}
top_products_awareness(survey, Region.Northeast.name, 5)
```

#### Part B

What are the top 5 products by advocacy rates among female respondents who earn at least $100,000?

```{r q2_b}
top_products_advocacy(survey, Gender.Female.name, 100000, top_n = 5)
```





### Q3:  Overall Brand Perceptions {.tabset}

What are the top 5 brands by the overall average perception?


```{r q3}
# Compute average scores, removing missing values
average_perceptions <- survey[, lapply(.SD, mean, na.rm = TRUE), .SDcols = all_perceptions, by = .(get(Product.name))]

# Rename the "get" column to the desired variable name
setnames(average_perceptions, "get", Product.name)

# Invert the scores for negative perceptions
average_perceptions[, (negative_perceptions) := lapply(.SD, function(x) 10 - x), .SDcols = negative_perceptions]

# Compute the mean of all perception scores
average_perceptions[, Overall_Average_Perception := rowMeans(.SD, na.rm = TRUE), .SDcols = all_perceptions]
average_perceptions[, Overall_Average_Perception := round.numerics(Overall_Average_Perception,2)]

# Rank the brands in decreasing order of Overall Average Perception scores
top_brands <- average_perceptions[order(-Overall_Average_Perception)][1:5, .(Product, Overall_Average_Perception)]

# Display the results for the top 5 brands
knitr::kable(top_brands, caption = "Top 5 Brands by Overall Average Perception Scores")

```


### Q4: Gaps in Outcomes {.tabset}


#### Part A

Which 5 products have the largest gap between the rate of consumption and the rate of awareness?  This would correspond to a formula of Difference = 100 * (Average Consumption - Average Awareness).  (Please use this exact formula.  Do not use the absolute value.  Focus only on the highest positive gaps.)  Display a bar graph showing the 5 largest differences in decreasing sorted order.

```{r q4}
# Apply functions to calculate scores for each binary outcome
for (outcome in binary_outcomes) {
  survey <- calculate_binary_scores(survey, outcome)
}

for (outcome in integer_outcomes) {
  max_score <- max(survey[, .(max_score = max(get(outcome), na.rm = TRUE)), by = Product.name]$max_score)
  survey <- calculate_integer_scores(survey, outcome, max_score)
}
```

```{r q4_a}
# Part A: Calculate the gap between the rate of consumption and the rate of awareness
gap_consumption_awareness <- survey[, .(Average_Consumption = mean(Consumption_Score, na.rm = TRUE),
                                       Average_Awareness = mean(Awareness_Score, na.rm = TRUE)),
                                    by = Product.name]

gap_consumption_awareness[, Consumption_Awareness_Difference := round.numerics(100 * (Average_Consumption - Average_Awareness),2)]

# Select the top 5 products with the largest differences
top_consumption_awareness <- gap_consumption_awareness[order(-Consumption_Awareness_Difference)][1:5, .(get(Product.name), Consumption_Awareness_Difference)]

# Order the top 5 products in decreasing order
top_consumption_awareness <- gap_consumption_awareness[order(-Consumption_Awareness_Difference)][1:5, .(Product, Consumption_Awareness_Difference)]

# Create a bar graph with ordered products and labels
bar_plot_consumption_awareness <- ggplot(top_consumption_awareness, aes(x = reorder(Product, -Consumption_Awareness_Difference), y = Consumption_Awareness_Difference)) +
  geom_bar(stat = "identity", fill = "lightcoral") +
  geom_text(aes(label = sprintf("%.2f%%", Consumption_Awareness_Difference)), vjust = -0.5, size = 3.5) +  # Add percentage labels
  labs(title = "Top 5 Products with Largest Gap: Consumption vs Awareness",
       x = "Product",
       y = "Difference (%)") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate x-axis labels for better readability

# Display the bar graph
print(bar_plot_consumption_awareness)
```

#### Part B

Which 5 products have the largest gap between the rate of awareness and the average satisfaction?  This would correspond to a formula of Difference = 100 * (Average Awareness - Average Satisfaction).  (Please use this exact formula.  Do not use the absolute value.  Focus only on the highest positive gaps.)  Display a bar graph showing the 5 largest differences in decreasing sorted order.

```{r q4_b}
# Part A: Calculate the gap between the rate of awareness and rate of satisfaction
gap_awareness_satisfaction <- survey[, .(Average_Satisfaction = mean(Satisfaction_Score, na.rm = TRUE),                                          Average_Awareness = mean(Awareness_Score, na.rm = TRUE)),
                                     by = Product.name]

gap_awareness_satisfaction[, Awareness_Satisfaction_Difference := round.numerics(100 * (Average_Awareness - Average_Satisfaction),2)]

# Select the top 5 products with the largest differences
top_awareness_satisfaction <- gap_awareness_satisfaction[order(-Awareness_Satisfaction_Difference)][1:5, .(get(Product.name), Awareness_Satisfaction_Difference)]

# Order the top 5 products in decreasing order
top_awareness_satisfaction <- gap_awareness_satisfaction[order(-Awareness_Satisfaction_Difference)][1:5, .(Product, Awareness_Satisfaction_Difference)]

# Create a bar graph with ordered products and labels
bar_plot_awareness_satisfaction <- ggplot(top_awareness_satisfaction, aes(x = reorder(Product, -Awareness_Satisfaction_Difference), y = Awareness_Satisfaction_Difference)) +
  geom_bar(stat = "identity", fill = "lightcoral") +
  geom_text(aes(label = sprintf("%.2f%%", Awareness_Satisfaction_Difference)), vjust = -0.5, size = 3.5) +  # Add percentage labels
  labs(title = "Top 5 Products with Largest Gap: Awareness vs Satisfaction",
       x = "Product",
       y = "Difference (%)") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate x-axis labels for better readability

# Display the bar graph
print(bar_plot_awareness_satisfaction)

```


### Q5: Aggregated Engagement {.tabset}

#### Part A

How much impact does respondent's overall trends in awareness have for that person's awareness with Buzzdial phones?

```{r q5_a}
# Call the calculate aggregated engagement
survey <- calc_agg(survey, Awareness.name, Products.Buzzdial.name)

# Part A: Awareness model
aware_mod <- glm(Awareness ~ Age_Group + Gender + Income_Group + Region + 
                  Persona + Aggregated_engagement, data = subset(survey, Product ==        Products.Buzzdial.name), 
                 family = binomial())

# Get tidy summary of the model with Odds Ratios and CIs
aware_mod_summary <- tidy(aware_mod, exponentiate = TRUE, conf.int = TRUE)

# Display the table
print(aware_mod_summary)
```

#### Part B

How much impact does respondent's overall trends in satisfaction have for that person's satisfaction with Buzzdial phones?

```{r q5_b}
survey <- calc_agg(survey, Satisfaction.name, Products.Buzzdial.name)

sat_mod <- lm(Satisfaction ~ Age_Group + Gender + Income_Group + Region +
               Persona + Aggregated_engagement, data = subset(survey, Product == Products.Buzzdial.name))

# Get tidy summary of the model with coefficients, CIs, and p-values
sat_mod_summary <- tidy(sat_mod, conf.int = TRUE)

# Display the table
print(sat_mod_summary)
```

